---
title: "Project One: Environmental Analysis"
subtitle: "We did something great here"
date:  'Last update: `r format(Sys.Date(), " %Y-%m-%d")`'
author: "Yihui Xie & Rachel Carson | MPCA"
output:
  tufte::tufte_html: 
    tufte_variant: "envisioned"
    toc: true
    toc_depth: 1
    css:  "report_style.css"
    includes:
      before_body: banner.html
toc-title: "Table of Contents"
bibliography: skeleton.bib
---

```{r setup, include=F}
knitr::opts_chunk$set(message=F, warning=F, comment = "")
```


# Summary

`r tint::newthought("The goal")` of this project is to identify the four Pokemon^[Pokemon are a new invasive species in MN. See [Pokemen explosion in MN](https://en.wikipedia.org/wiki/Pok%C3%A9mon).] that are polluting the local stream and causing it to glow purple on several occasions, documented on the following dates:

- `July 12, 2020`
- `July 18, 2020`
- `July 23, 2020`


> **Project details**   
>
> Where:  
> Who:  
> What:  


# <span class="header-section-number">1</span> Data overview

<hr class="numbered">

The table below shows a glimpse of the results. _(You can add a caption to your table by adding `caption="My caption"` to the `kable()` function as below.)_

```{r, echo=T}
knitr::kable(mtcars[1:6, 1:6], caption = '**TABLE 1.** A subset of mtcars.')
```


## Data sources

The data were downloaded from the following online resources:

1. US EPA
1. MN GEO Commons
1. TEMPO

```{r, eval=F}
library(tidyverse)

# Download data
data <- read_csv("")

```


## DELTA is where data lives 

 
::: {.fullwidth}

## Data dictionary 

Explore all the data available in DELTA with the [RAINIER documentation](http://rainier/documentation/DataDictionary/DELTAW/index.html) pages.

** A raw Markdown table ** 

| Column  |  Description   |  Example value      |
|:-|:---|:---|
|`geoid` |  Unique ID assigned to each Pokemon.      |  _`2430262`_ |    
|`lat  ` |  Latitude coordinate of object's center.  | _`-94.021`_  |   
|`lon  ` |  Longitude coordinate of object's center. |  _`44.521`_  | 


## Data glimpse
For this project, facilities were pulled from MPCA's TEMPO database.   
You can use the `mpcadb` package to access TEMPO from R.

```{r mpcadb}
library(mpcadb) #remotes::install_github("MPCA-data/mpcadb")

## TEMPO AI's
# Get a subset of AI names with get_ai()
ai_names <- get_ai(ai = c(420, 564, 878), keep_alt_names = F)
```

We use the `DT` package to create scrollable, searchable, interactive web tables. The default for `DT` tables is to extend the full width of the page.

```{r full-table} 
library(DT)
library(dplyr)

# Keep the alternative name columns
ai_names <- get_ai(ai = c(420, 564, 878), 
                   keep_alt_names = T)

# Drop the underscores from the column names
names(ai_names) <- names(ai_names) %>% gsub("_", " ", .)

# Scrolly pretty table
DT::datatable(ai_names, 
              caption = 'TABLE 2. Selected facilities.',
              rownames = F,
              options = list(pageLength = 4, 
                             scrollX    = T, 
                             dom = 'ftip')) 
```

:::

## _(help)_ Access spatial data from MN's GIS Rest API

## _(help)_ Read data from: PDF's, Excel, Access 


# <span class="header-section-number">2</span> Charts

<hr class="numbered">


To place figures in the margin you can use the **knitr** chunk option `fig.margin=TRUE`.

Here's an example using a fuel efficiency chart: 

`{r fig-margin, fig.margin=TRUE, fig.cap="MPG vs Horsepower, colored by transmission."}`

```{r fig-margin, fig.margin = TRUE, fig.cap = "**FIG 1.**   MPG vs horsepower, colored by transmission.", fig.width=3.5, fig.height=3.5}
library(ggplot2)
library(mncolors) #remotes::install_github("MPCA-data/mncolors")

mtcars <- mtcars

mtcars$Transmission <- factor(mtcars$am, 
                              labels = c('automatic', 
                                         'manual'))

ggplot(mtcars, aes(hp, mpg, color = Transmission)) +
  geom_point() + 
  geom_smooth() +
  scale_color_mn(palette = "accent", reverse = T) +
  theme(legend.position = 'top')
```


## MN Colors

::: {.fullwidth}

Here's one way to set the colors for your plots to align with the MN state brand.

```{r set-colors}
library(mncolors) #remotes::install_github("MPCA-data/mncolors") 
library(ggplot2)
library(hrbrthemes)

ggplot(diamonds, aes(carat, price)) +
  geom_smooth(aes(color = cut), size = 1.5, show.legend = F) +
  scale_color_mn(palette = "green") +
  facet_wrap(vars(cut), nrow = 1) +
  labs(title    = "Increasing cost of cleanups",
       subtitle = "Brownfield site classifications",
       caption  = "Source: EPA Data Mart 2018",
       x        = "Site score") +
  scale_y_comma() +
  theme_ipsum_rc() +
  theme(plot.title   = element_text(color = mncolors(5, "blue")[5]),
        plot.caption = element_text(color = mncolors(5, "blue")[2], 
                                    face  = 'bold'))
```

:::


# <span class="header-section-number">3</span> Analysis

<hr class="numbered">

```{marginfigure}
  for $x$ in $[a, b]$:
$$\frac{d}{dx}\left( \int_{a}^{x} f(u)\,du\right)=f(x)$$
```

We used the equation on the right to scale the Pokemon contribution to its relative size and spatial distribution in the watershed.
  
  
To set figures to span the entire page use the `{r}` chunk option `fig.fullwidth = TRUE`.

```{r fig-fullwidth, fig.width=10, fig.height=2, fig.fullwidth=T, fig.cap = "**FIG 2.** A full width figure."}

ggplot(diamonds, aes(carat, price)) + geom_smooth() +
  facet_grid(~ cut)
```


## _(help)_ Non-detect and Censored data summaries

## _(help)_ Multivariate predictions


# <span class="header-section-number">4</span> Maps

<hr class="numbered">

Leaflet maps are an easy way to add interactive maps to your report. Here's an example displaying the polygon shapefile of tribal nations located across MN.


```{marginfigure}
<br>
<br>
  
Find shapefiles and spatial data in the [MN GEOCOMMONS](https://gisdata.mn.gov/).
```

```{r full-map, fig.width=8.5, fig.height=5, fig.fullwidth=T, fig.cap="_Ref. MPCA Geocommons..._"}
library(mpcaej) #remotes::install_github("MPCA-data/mpcaej")
library(leaflet)
library(sf)
library(tidyverse)

ej_shapes    <- ej_shapes

tribal_areas <- tribe_shapes

#------ Map the polygons ---------#
leaflet(st_transform(tribal_areas, 4326)) %>%
  addProviderTiles(providers$Stamen.TonerLines,
                   options = providerTileOptions) %>%
  addProviderTiles(providers$CartoDB.Voyager,
                   options = providerTileOptions(opacity = 0.8)) %>%
  addPolygons(color        = "purple",
              weight       = 1,
              smoothFactor = 1.4,
              opacity      = 0.9,
              fillOpacity  = 0.2) 
```

 

# <span class="header-section-number">5</span> Site maps

<hr class="numbered">

**Map markers**  
This is a map of the project monitoring sites dispersed around St. Paul.
```{r, fig.width=6, fig.height=3}
sites <- read_csv('https://raw.githubusercontent.com/MPCA-air/aqi-watch/master/data-raw/locations.csv')

sites <- filter(sites, str_detect(`Site Name`, "Paul"))

# Add Markers and popup info
leaflet(sites) %>%
  addProviderTiles(providers$CartoDB) %>%
  addMarkers(popup = ~`Site Name`)
```

<br>

**Circle markers**  
The circles show the monitoring range of the monitors. 
```{r, fig.width=6, fig.height=3}
# Add Darkness
leaflet(sites) %>%
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  addCircleMarkers(label = ~`Site Name`)
```

<br>

**Labeling a single site**  
The specific site highlighted below has concerning results.
```{r, fig.width=6, fig.height=3}
# Add Darkness
leaflet(sites) %>%
  addProviderTiles(providers$CartoDB.DarkMatter) %>%
  addCircleMarkers(label = ~`Site Name`) %>%
  addCircleMarkers(data   = sites[3, ],
                   color  = "hotpink",
                   radius = 15,
                   label  = ~`Site Name`,
                   labelOptions = labelOptions(noHide   = T, 
                                               textsize = "15px"))
```



# <span class="header-section-number">6</span> Collapsible content

<hr class="numbered">

To hide a long list or table you can use `<details> and <summary>` to create hidden drop-down content. Adding the following creates a drop-down window in your document that starts collapsed, but expands when the reader selects it.


```md
<details>
<summary> Click to see the Loooooong list </summary>

 ...this is hidden, collapsable content...

- fish
- bird
- toad
- stone
 
</details>
```


__And here it is:__

<details>
<summary> Click to see the Loooooong list </summary>
 
 ...this is hidden, collapsable content...

- fish
- bird
- toad
- stone

</details>


# <span class="header-section-number">7</span> Conclusion

<hr class="numbered">

You can add quotes or highlight some text with the `tint::quote_footer()` function.

> _I can win an argument on any topic, against any opponent. People know this, and steer clear of me at parties. Often, as a sign of their great respect, they don't even invite me._
>
> `r tint::quote_footer('--- Dave Barry')`


## References

- 2012, A
- 2015, B
- 2018, C


```{r bib, include=F}
# KEEP AT END OF THE DOCUMENT TO CREATE A LOCAL bib FILE FOR PKGS USED
knitr::write_bib(sub("^package:", "", 
                     grep("package", search(), value=TRUE)),
                 file='skeleton.bib')
```

